Degrees Draft Syllabus

### 2023-04-06 Bookdown Syllabus/Bookdown Syllabus.Rmd
Add Bookdown version of the syllabus

---
title: "Degrees Draft Syllabus"
author: "Reggie Gilliard"
date: "11/29/2022"
output:
  html_document:
    toc: TRUE
    toc_depth: 2
    toc_float: TRUE

---

>>>>

---
title: "Degrees Draft Syllabus"
author: "Reggie Gilliard"
date: "11/29/2022"
output:
  bookdown::gitbook:
    lib_dir: assets
    split_by: section
    config:
      toolbar:
        position: static
  bookdown::pdf_book:
    keep_tex: true
  bookdown::html_book:
    css: toc.css
documentclass: book
---
